%------------------------------------------------------------------------------
% CV in Latex
% Author : Charles Rambo
% Based off of: https://github.com/sb2nov/resume and Jake's Resume on Overleaf
% Most recently updated version may be found at https://github.com/fizixmastr 
% License : MIT
%------------------------------------------------------------------------------

\documentclass[A4,11pt]{article}
%\documentclass[letterpaper,11pt]{article} %For use in US
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{xcolor}
\input{glyphtounicode}

\begin{comment}
I am by no means a professional when it comes to the CV's/resumes, I have
received various trainings on how to write a CV and resume from my high 
school, as well as the Austin College and University of Eastern Finland's
career counseling departments. As I intend to share my CV as a template, I 
feel that it is my responsibility to provide explanations of my work.
\end{comment}


%-----FONT OPTIONS-------------------------------------------------------------
\begin{comment}
The font of the document will impact not just how readable it is, but how it is
perceived. In the "The Craft of Scientific Writing" by Michael Alley, shares a
common fonts for publication as well as their use. I have chosen to use
Palatino for its legibility, some others are given below. There is far too much
about typography to discus here. Note: serif fonts have short projecting
strokes, sans-serif fonts are sans (without) these strokes.
\end{comment}


% serif
 \usepackage{palatino}
% \usepackage{times} %This is the default as well
% \usepackage{charter}

% sans-serif
% \usepackage{helvet}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

%-----PAGE SETUP---------------------------------------------------------------

% Adjust margins
\addtolength{\oddsidemargin}{-1cm}
\addtolength{\evensidemargin}{-1cm}
\addtolength{\textwidth}{2cm}
\addtolength{\topmargin}{-1cm}
\addtolength{\textheight}{2cm}

% Margins for US Letter size
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
%\addtolength{\topmargin}{-.5in}
%\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0cm}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that .pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-----CUSTOM COMMANDS FOR FORMATTING SECTIONS----------------------------------
\newcommand{\CVItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\CVSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\CVSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \text{\small#1} & \text{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\CVSubItem}[1]{\CVItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\CVSubHeadingListStart}{\begin{itemize}[leftmargin=0.5cm, label={}]}
% \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} % Uncomment for US
\newcommand{\CVSubHeadingListEnd}{\end{itemize}}
\newcommand{\CVItemListStart}{\begin{itemize}}
\newcommand{\CVItemListEnd}{\end{itemize}\vspace{-5pt}}

%------------------------------------------------------------------------------
% CV STARTS HERE  %
%------------------------------------------------------------------------------
\begin{document}

%-----HEADING------------------------------------------------------------------
\begin{comment}
In Europe it is common to include a picture of ones self in the CV. Select
which heading appropriate for the document you are creating.
\end{comment}


% Without picture
\begin{center}
   \textbf{\Huge \scshape Imran Hussain Barbhuiya} \\ \vspace{1pt} %\scshape sets small capital letters, remove if desired
   \small Full Stack Developer Building the Future of Web and Mobile \\
   \small +91 6000423502 $|$ 
   \href{mailto:imranbarbhuiya.fsd@gmail.com}{\underline{imranbarbhuiya.fsd@gmail.com}} $|$\\
   % Be sure to use a professional *personal* email address
   \href{https://linkedin.com/in/imranbarbhuiya}{\underline{\color{blue} Linkedin}} $|$
   % you should adjust you linked in profile name to be professional and recognizable
   \href{https://github.com/imranbarbhuiya}{\underline{\color{blue} Github}} $|$
   \href{https://parbez.me/resume}{\underline{\color{blue} Website}} $|$
   \small India
\end{center}



\begin{comment}
This CV was written for specifically for positions I was applying for in
academia, and then modified to be a template.

A standard CV is about two pages long where as a resume in the US is one page.
sections can be added and removed here with this in mind. In my experience, 
education, and applicable work experience and skills are the most import things
to include on a resume. For a CV the Europass CV suggests the categories: Work
Experience, Education and Training, Language Skills, Digital Skills,
Communication and Interpersonal Skills, Conferences and Seminars, Creative Works
Driver's License, Hobbies and Interests, Honors and Awards, Management and
Leadership Skills, Networks and Memberships, Organizational Skills, Projects,
Publications, Recommendations, Social and Political Activities, Volunteering.

Your goal is to convey a who, what , when, where, why for every item you share. 
The who is obviously you, but I believe the rest should be done in that order.
For example below. An employer cares most about the degree held and typically 
less about the institution or where it is located (This is still good 
information though). Whatever order you choose be consistent throughout.
\end{comment}

%-----WORK EXPERIENCE----------------------------------------------------------
\begin{comment}
try to briefly explain what you did and why it is relevant to the position you
are seeking
\end{comment}

\section{Work Experience}
  \CVSubHeadingListStart
%    \CVSubheading %Example
%      {What you did}{When you worked there}
%      {Who you worked for}{Where they are located}
%      \CVItemListStart
%        \CVItem{Why it is important to this employer}
%      \CVItemListEnd

    \CVSubheading
      {TEC Spartans}{Nov 2023 -- Present}
      {Mobile App Developer}{\href{https://theesports.club/spartans}{\underline{\color{blue} Website}}}
      \CVItemListStart
        \CVItem{Developed the TEC Spartans mobile app to streamline campaign and event participation.}
        \CVItem{Implemented features such as push notifications, user authentication, and real-time updates.}
        \CVItem{Used Expo Updates to enable over-the-air updates, ensuring users always have the latest version.}
        \CVItem{Integrated real-time chat functionality using Pusher, allowing users to communicate with each other and the organization.}
        \CVItem{Built a custom CI/CD pipeline using GitHub Actions and a self-hosted Mac mini, enabling builds triggered by push, PR, comment, and workflow\_dispatch. Automated publishing to the iOS App Store or S3 for local download, reducing cloud costs while maintaining full build automation.}
        \CVItem{Developed using Expo React Native and NestJS with TypeScript.}
        \CVItem{Additionally contributed to backend system development.}
      \CVItemListEnd

    \CVSubheading
      {Sofi}{Oct 2021 -- Present}
      {Founding Engineer}{\href{https://sofi.gg/}{\underline{\color{blue} Website}}}
      \CVItemListStart
        \CVItem{Led full web development for an anime-themed game application serving over \textbf{30,000 daily active users}, with a total reach of \textbf{600,000 users} across 15+ countries.}
        \CVItem{Optimized Sofi’s performance using a diverse stack, improving user retention and latency. As the main runtime, Node.js manages the workload, orchestrating over 120 shards to distribute the load effectively.}
        \CVItem{Leveraged Rust for high-performance image generation, utilizing multi-core processing and uses IPC for inter-process communication with TypeScript.}
        \CVItem{Created a \textbf{Photoshop-style album editor} with advanced features like drag-and-drop, multi-selection, rotation, and rich customization tools.}
        \CVItem{Implemented payment systems {\href{https://shop.sofi.gg/}{(link)}} supporting one-time gem purchases and recurring patron subscriptions via PayPal and Lemon Squeezy.}
      \CVItemListEnd

    \CVSubheading
      {OBScoreboard}{Jan 2025 -- June 2025}
      {Full Stack Developer}{\href{https://app.obscoreboard.com/}{\underline{\color{blue} Website}}}
      \CVItemListStart
        \CVItem{Developed a platform for live game overlays and remote control tools for OBS streamers.}
        \CVItem{Used Firebase Datastore and Live DB to support real-time overlay draft saving, multi-device editing, and synchronized live updates.}
        \CVItem{Leveraged SVG with React to dynamically display and update overlay content.}
        \CVItem{Built using NextJS, TypeScript, and Firebase.}
        \CVItem{Enabled real-time features and remote control functionality.}
      \CVItemListEnd

      \CVSubheading
        {R.O.T.I.}{Oct 2021 -- Feb 2024}
        {Co-founder}{\href{https://rotibot.xyz/}{\underline{\color{blue} Link}}}
        \CVItemListStart
          \CVItem{Built and scaled a Discord moderation bot used in over 50,000 servers.}
          \CVItem{Led product, engineering, and community efforts as co-founder.}
          \CVItem{Developed in TypeScript.}
        \CVItemListEnd

    \CVSubheading
      {Flatshare (Inactive)}{2023}
      {Backend Developer}{\href{https://joinflatshare.com/}{\underline{\color{blue} Website}}}
      \CVItemListStart
        \CVItem{Worked as backend developer for Flatshare, a mobile app connecting users to potential flatmates in India.}
        \CVItem{Designed and built backend systems using Express.js.}
        \CVItem{Supported the successful launch of the Android app on the Play Store.}
        \CVItem{Created Metabase dashboards to visualize backend metrics and user activity using custom mongodb aggregations.}
      \CVItemListEnd

    % \CVSubheading
    %   {CTO \& Lead Developer}{2024 -- Present}
    %   {Xofi (Under Development)}{\href{https://xofi.gg/}{\underline{\color{blue} Website}}}
    %   \CVItemListStart
    %     \CVItem{Overseeing technical direction and full-stack development of an anime merchandise e-commerce platform.}
    %     \CVItem{Developing using NextJS, NestJS (Fastify), and PayloadCMS.}
    %     \CVItem{Responsible for overall architecture and long-term technical strategy as CTO.}
    %   \CVItemListEnd

      \CVSubheading
        {Adwings CRM}{Feb 2025 - Apr 2025}
        {Full Stack Developer}{\href{https://adwingscrm.com/}{\underline{\color{blue} Link}}}
        \CVItemListStart
          \CVItem{Developed a website for real-time leads management with browser push notifications.}
          \CVItem{Implemented a real-time chat interface for seamless communication.}
        \CVItemListEnd

  \CVSubHeadingListEnd

\section{Projects}
  \CVSubHeadingListStart

    \CVSubheading
    {{Video Analyzer} $|$ \emph{\small{Typescript, AI SDK}}}{}
    {Developed an AI-powered chat tool for The Esports Club to analyze YouTube and Instagram Reels.\\Automatically fetches or generates video transcripts, retrieves comments,\\and uses RAG to answer context aware questions, helping brands verify sponsored content.}{}

    \CVSubheading
      {{Ran Programming Language} $|$ \emph{\small{Go}}}{
   \href{https://github.com/imranbarbhuiya/ran/}{\underline{\color{blue} Link}}}
      {A programming language built from scratch in Go, inspired by compiler and interpreter design books.}{}

    \CVSubheading
      {{Tagscript} $|$ \emph{\small{Typescript}}}{
   \href{https://tagscript.js.org/}{\underline{\color{blue} Link}}}
      {A dynamic string interpreter allowing logic and customization in content. Ported from Python to TypeScript.}{}

    \CVSubheading
      {{esbuild-plugins-node-modules-polyfill} $|$ \emph{\small{Typescript}}}{
   \href{https://github.com/imranbarbhuiya/esbuild-plugins-node-modules-polyfill}{\underline{\color{blue} Link}}}
      {An esbuild plugin for polyfilling Node.js core modules and injecting global objects.}{}
      {}{$ \newline $}{}{Used by major frameworks including Remix and Cloudflare.}

    \CVSubheading
      {{typedoc-plugin-external-link} $|$ \emph{\small{Typescript}}}{
   \href{https://github.com/imranbarbhuiya/typedoc-plugin-external-link}{\underline{\color{blue} Link}}}
      {A plugin for adding external module links in Typedoc documentation.}{}

    \CVSubheading
      {{css-tailwind-codegen} $|$ \emph{\small{Typescript}}}{
   \href{https://www.figma.com/community/plugin/1295012016362159423/css-tailwind-codegen}{\underline{\color{blue} Link}}}
      {A Figma plugin that generates Tailwind CSS from devmode styles.}{}

     \CVSubheading
      {{i18n-validate} $|$ \emph{\small{Typescript}}}{
    \href{https://github.com/imranbarbhuiya/i18n-validate}{\underline{\color{blue} Link}}}
      {A tool that statically analyzes TypeScript codebases to validate i18n usage,\\detecting invalid translation keys and incorrect or missing variable usage.}{}

     \CVSubheading
      {{React Native Headless Mention Input} $|$ \emph{\small{Typescript}}}{
   \href{https://github.com/imranbarbhuiya/react-native-headless-mention}{\underline{\color{blue} Link}}}
      {An input component with mention support, built for TEC Spartans’ chat functionality.}{}

    \CVSubheading
      {{Other Open Source Projects}}{
   \href{https://github.com/imranbarbhuiya?tab=repositories\&q=\&type=source\&language=\&sort=stargazers}{\underline{\color{blue} Link}}}
      {Additional open-source work and community contributions.}{}

  \CVSubHeadingListEnd

\section{Skills}
  \begin{itemize}[leftmargin=0.5cm, label={}]
    \small{\item{
      \textbf{Languages}{: TypeScript, JavaScript, Rust, Python, Go, Dart} \\
      \textbf{Frameworks and Libraries}{: React, NextJS, React Native, Expo, Tauri, NestJS, Express.js, Fastify, WebSocket, Socket.io, Pusher, Flutter} \\
      \textbf{Databases}{: MongoDB, PostgreSQL, Redis, SQLite, MySQL} \\
      \textbf{Cloud Platforms}{: Vercel, Hetzner, Firebase, Supabase, AWS} \\
    }}
  \end{itemize}

% -----EDUCATION----------------------------------------------------------------
% \section{Education}
%   \CVSubHeadingListStart
%       \CVSubheading
%         {{Bachelor of Science $|$ \emph{\small{Physics}}}}{Incomplete, final year dropout}
%         {Gurucharan College, Silchar}{India}
%   \CVSubHeadingListEnd

\section{Extracurricular Activities}
  \CVSubHeadingListStart
    \CVSubheading
      {Teacher (Part Time)}{2023 -- 2025}
      {Al Mubaswir English Academy}{\href{https://almubaswirenglishacademy.com/}{\underline{\color{blue} Website}}}
      \CVItemListStart
        \CVItem{Taught Science, Mathematics, and Computer Science to students of classes IX and X.}
        \CVItem{Provided academic support and mentorship to guide students through their learning journey.}
      \CVItemListEnd
  \CVSubHeadingListEnd
    
%------------------------------------------------------------------------------
\end{document}